% HERE i WILL TALK ABOUT HOW PROCRASTINATION IS LINKED TO NEGATIVE THOUGHTS ABOUT ONESELF
% AND HOW IT CAN BE A SELF FULFILLING PROPHECY

Expectancy refers to an individual's beliefs about their ability to complete the task at hand.
A high expectancy implies that the individual believes they are capable of completing the task and will be successful in doing so,
while a low expectancy suggests that the person does not believe they can reach their desired outcome. \cite{Steel2007}

% Negative thoughts = procrastination
\subsubsection{Negative thoughts and procrastination}

A strong correlation between procrastination and fear of failure has been observed. \cite{Flett2012Dec}
Flett et al \cite{Flett2012Dec} discovered a strong correlation between individuals that score highly on the MaSQ(
a 77-item self-report questionnaire that assesses depressive) anxious and mixed symptomatology, and a tendency to procrastinate.
The study suggests a strong correlation between automatic thoughts about procrastination and
broader negative automatic thoughts about ourselves.
This means that individuals who have negative thoughts about themselves are more likely to procrastinate, and vice versa.
This information may be useful in helping people understand why they procrastinate and how to address the issue.

% ANXIETY = procrastination
It is interesting to note that individuals who are prone to stress and anxiety may view their procrastination tendencies as a
personal shortcoming. This is because they may focus on the negative consequences of their actions,
such as the feeling of guilt or anxiety that comes with delaying a task.
In this sense, procrastination can be seen as a vicious cycle in which individuals feel bad about themselves for not meeting their goals,
which only leads to more procrastination.\cite{Flett2012Dec}

The fact that there is a link between procrastination and stress \cite{Sirois2013Feb} is not surprising,
due to the consequences of procrastination. More interesting though,
is the fact that previous research found a correlation between procrastination and lack of self compassion \cite{Sirois2013Feb}
Consequently, since people who struggle with procrastination may also find
it difficult to be compassionate about themselves. Procrastination leads to negative thoughts and feelings about oneself, which can then lead to the urge to procrastinate even more.

\subsubsection{Procrastination as a self fulfilling prophecy}
To conclude,the research points to the phenomenon, that individuals who expect to fail at a task are more
likely to procrastinate as they attempt to avoid the feelings of disappointment,
frustration, and even shame that come with failure.
This is because they lack the motivation to put in the effort required to complete the task,
believing that their efforts will lead them nowhere.
By avoiding the task altogether, they can protect their ego from potential failure.