%TODO : these people found correlationbetween procrastination and fear of failure



%here I will talk about how procrastination is linked to negative thoughts about oneself 
There is a strong correlation between procrastination and fear of failure. \cite{Flett2012Dec}
%TODO: because you want to avoid negative feelings

Flett et al \cite{Flett2012Dec} discovered a strong correlation between people that score highly on the MaSQ(
a 77-item self-report questionnaire that assesses depressive) anxious and mixed symptomatology, and a tendency to procrastinate.

% Negative thoughts = procrastination
The study suggests a strong correlation between automatic thoughts about procrastination and broader negative automatic thoughts about ourselves. This means that individuals who have negative thoughts about themselves are more likely to procrastinate, and vice versa. This information may be useful in helping people understand why they procrastinate and how to address the issue.

% ANXIETY = procrastination
It is interesting to note that individuals who are prone to stress and anxiety may view their procrastination tendencies as a personal shortcoming. This is because they may focus on the negative consequences of their actions, such as the feeling of guilt or anxiety that comes with delaying a task. In this way, procrastination can be seen as a vicious cycle in which individuals feel bad about themselves for not meeting their goals, which only leads to more procrastination.


\cite{Flett2012Dec}

The fact that there is a link between procrastination and stress \cite{Sirois2013Feb} is not surprising, due to the consequences of procrastination. More interesting though, is the fact that previous research found a correlation between procrastination and lack of self compassion \cite{Sirois2013Feb}
Consequently, since people who struggle with procrastination may also find
it difficult to be compassionate about themselves. Procrastination leads to negative thoughts and feelings about oneself, which can then lead to the urge to procrastinate even more.

